{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-23 brains-protocol.tex
Start comments on results for feature variation

>>>>

\rk{Might want to globally add $y = x$? Defines areas above/below $y = x$ and areas above/below $H_0$}

\begin{itemize}
    \item Clustering: flat, no dependency. But negative bias, which corresponds to literature on word production.
    \item AoA: global negative bias, also consistent with literature. Question: on one side, effect w.r.t. $H_0$ is weaker for higher AoA, but if you compare to $y = x$, it's not that clear.
    \item Frequency: very strong positive bias, ok. Now extreme high-frequency words have a different pattern (maybe a third category at the opposite of the very low-frequency words?): even if above $H_0$, they're brought quite lower than their original value (complexified?)
    \item Number of phonemes and Number of synonyms: expanding behavior (but check with $y = x$): lower goes to lower, higher goes to higher.
\end{itemize}
